CRUSE to Safe Cycling in Ireland

### 2023-09-29 paper.qmd
Add link supporting 3% figure

A proactive approach to the development of cycling policy and infrastructure is taking place in Ireland.
The main framework underpinning these efforts is the Climate Action Plan[^2] and The National Development Plan[^3]
. Strategic alignment is also outlined by the Phoenix Park Transport and Mobility Options Study, which highlights public support for active travel interventions: "83% of respondents supported enhanced walking and cycling facilities"
.

>>>>

A proactive approach to the development of cycling policy and infrastructure is taking place in Ireland.
The main framework underpinning these efforts is the Climate Action Plan[^2] and The National Development Plan[^3].
Strategic alignment is also outlined by the Phoenix Park Transport and Mobility Options Study, which highlights public support for active travel interventions: while only 3% of trips in Ireland are made by cycling according to the latest Census data from 2016,^[
https://assets.gov.ie/42950/f789b2fcfb144441822f58236986eeea.pdf
] "83% of respondents supported enhanced walking and cycling facilities".
